Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-06-03 sections/3algebras.tex
Todo is partially done.

Now that we have introduced all the varieties of factorization algebras, it's a natural and useful question to ask what the $\infty$-operad governing them is. For prefactorization algebras, the answer comes by definition, but this is not the case for factorization algebras. In the case of stratified manifolds, we will show that the $\infty$-operad that governs locally constant factorization algebras can be taken to be $\disk_{/M}$, and the one that governs ordinary factorization algebras can be taken to be $\disk[r]_{/M}$. This result is immensely helpful in relating factorization algebras to results in the area of disk algebras. We will see one such example in \Cref{ch:gluing_disk_alg}.

\begin{proposition}\label{prop:fh_disk_to_lcfa}
    Given a stratified manifold $M$ factorization homology provides a functor between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$
    %
    \begin{equation}
        \int : \alg{\disk_M} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC).
    \end{equation}
\end{proposition}

\begin{proof}
    We adopt a proof strategy similar to \cite[prop.3.14]{af_primer}. Unlike there, we work in the relative case of $\disk_{/M}$ instead of $\disk(\bstr)$. Since the $\infty$-category of factorization algebras is defined as a pullback, we will look for a commutative diagram involving $\alg{\disk_{/M}}$, so that, by the universal property of the pullback, we get the stated functor.

    We first observe that, by definition, the $\infty$-operad $\opens(M) := \mfld[r]_{/M}$. There are clear functors of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \xhookrightarrow{\ \ \ } \mfld_{/M} \xleftarrow{\ \ \ } \mfld[r]_{/M}.
    \end{equation}
    %
    At the level of algebras over them, they give rise to the commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}
            \alg{\disk_{/M}} (\catC) \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l] \arrow[r] & \mathsf{Fun}(\opens(M), \catC),
        \end{tikzcd}
    \end{equation}
    %
    where the vertical arrows are forgetful functors. Factorization homology as a left Kan extension gives one the adjoints indicated below
    %
    \begin{equation}
        \begin{tikzcd}[row sep = large, column sep = large]
            \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10, "\int"] \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) \arrow[r, bend left=10, "\int"] & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l, bend left=10] \arrow[r] & \mathsf{Fun}(\opens(M), \catC).
        \end{tikzcd}
    \end{equation}
    %
    A result found in \cite[thm.1.2.5]{aft_localstrut} (where they use slightly different notation and call locally constant sheaves constructible) gives us the equivalence
    %
    \begin{equation}
        \csheaves[W](\mfld_{/M}, \catC) \simeq \csheaves[W, lc](\mfld[r]_{/M}, \catC) =: \csheaves[W, lc]_M(\catC),
    \end{equation}
    %
    which at the level of underlying functors, is exactly the restriction along the functor $\opens(M) \xrightarrow{} \mfld_{/M}$, so that we can append this to our commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}[row sep = large, column sep = large]
            \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10, "\int"] \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) \arrow[r, bend left=10, "\int"] \arrow[dr, dashed] & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l, bend left=10] \arrow[r] & \mathsf{Fun}(\opens(M), \catC) \\
            & \csheaves[W](\mfld_{/M}, \catC) \arrow[r, "\simeq"] \arrow[u] & \csheaves[W, lc]_M(\catC) \arrow[u].
        \end{tikzcd}
    \end{equation}
    %
    If we can find the dashed functor which makes the diagram commute, as indicated above, we would be done with the construction. This amounts to showing that the left Kan extension $\int F$ of a functor $F \in \mathsf{Fun}(\disk_{/M}, \catC)$ along $\disk_{/M} \xhookrightarrow{} \mfld_{/M}$ is automatically a Weiss cosheaf. By the definition of $\csheaves[W](\mfld_{/M}, \catC)$, this means that the restriction of $\int F$ to $\mathsf{Fun}(\mfld[r]_{/M}, \catC)$ satisfies the cosheaf property for every Weiss sieve $\mathscr{U} \subset (\mfld[r]_{/M})_{/e}$, where $e:N \xhookrightarrow{} M$ is an open embedding. Here we notice that for the Weiss property to even make sense, we are implicitly using \Cref{lem:double_slice}

    Since $\catC$ has all relevant colimits the left Kan extension $\int F$ is given pointwise by
    %
    \begin{equation}\label{eq:pointwiseKan}
        \int_e F \simeq \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC),
    \end{equation}
    %
    so what we need to show is that this colimit is equivalent to the colimit
    %
    \begin{equation}\label{eq:cosheaf_colim_relative}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \rightarrow \mfld_{/M} \xrightarrow{\int F} \catC),
    \end{equation}
    %
    for each covering sieve $\mathscr{U}$. Since we aren't actually trying to get the value of these colimits we can rewrite \Cref{eq:pointwiseKan} into the idiosyncratic form
    %
    \begin{equation}\label{eq:idiosync_form}
        \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC),
    \end{equation}
    %
    which is easier to compare to \Cref{eq:cosheaf_colim_relative}. Using the fact that $\disk[r]_{/M} \xrightarrow{} \disk_{/M}$ is a final functor, which is a consequence of \cite[prop.2.22]{aft_fhstrat}, and the equivalences of \Cref{lem:double_slice} we can rewrite \Cref{eq:idiosync_form} further into
    %
    \begin{align}
        \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC) \\ \simeq \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC).
    \end{align}
    %
    Denoting the functor $\mfld[r]_{/N} \simeq (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC$ by $K_F$ and comparing with \Cref{eq:cosheaf_colim_relative} we need to show
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C) \simeq \mathsf{colim} (\disk[r]_{/N} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C),
    \end{equation}
    %
    but this already follows from part 2 of the proof of \cite[prop.2.22]{af_primer}, and is equivalent to the statement that the functor
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{} \mfld[r] \xrightarrow{\disk_{/-}} \cat) \xrightarrow{} \disk_{/N},
    \end{equation}
    %
    is final.
\end{proof}

@@

From the proof of \Cref{prop:fh_disk_to_lcfa} it is easy to see that we can make a similar statement for ordinary factorization algebras too:

\begin{corollary}\label{cor:fh_disk_to_falg}
    Given a stratified manifold $M$ factorization homology provides a functor
    %
    \begin{equation}
        \int: \alg{\disk[r]_{/M}} (\catC) \xrightarrow{\ \ \ \ } \falg_{M} (\catC).
    \end{equation}
\end{corollary}

\begin{theorem}\label{thm:disk_alg=lcfa}
    For each stratified manifold $M$, the previously constructed factorization homology functor provides an equivalence of $\infty$-categories between $\disk_{/M}$-algebras and locally constant factorization algebras on $M$. Equivalently, the $\infty$-operad governing locally constant factorization algebras can be taken to be $\disk_{/M}$
    %
    \begin{equation}
        \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_M (\catC).
    \end{equation}
\end{theorem}

\begin{proof}
    To show essential surjectivity of $\int$, for each $F \in \lcfa_M (\catC)$ we will find an equivalence $\int F| \simeq F$ in $\lcfa_M (\catC)$, with $F|$ to be defined later. Since $\lcfa_M (\catC) \xrightarrow{} \alg{\opens(M)}$ is fully faithful, this amounts to finding equivalences of prefactorization algebras, namely a family of equivalences
    %
    \begin{equation}
        \int_U F| \xrightarrow[\simeq]{\ \ \phi (U) \ \ } F(U),
    \end{equation}
    %
    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which preserve the multiplicative structure (see \Cref{cd:fa_morphisms}). Since $F$ is a locally constant factorization algebra the functor
    %
    \begin{equation}
        \lcfa_M (\catC) \xrightarrow{} \csheaves[W, lc](\mfld[r]_{/M}, \catC) \simeq \csheaves[W](\mfld_{/M}, \catC) \xrightarrow{} \mathsf{Fun}(\mfld_{/M}, \catC),
    \end{equation}
    %
    which we omit in the notation, allows us to consider $F$ as a functor from $\mfld_{/M}$. Furthermore, since $\disk[r]_{/U}$ is a Weiss sieve we can write
    %
    \begin{align}
        F(U) &\simeq \mathsf{colim} (\disk[r]_{/U} \xrightarrow{} \disk[r]_{/M} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{F} \catC).
    \end{align}
    %
    By consulting the commutative diagram
    % 
    \begin{equation}
        \begin{tikzcd}
            \disk[r]_{/U} \arrow[d] \arrow[r] & \disk_{/U} \arrow[d] & \\
            \disk[r]_{/M} \arrow[d] \arrow[r] & \disk_{/M} \arrow[d] \arrow[r, "F|"] & \catC, \\
            \mfld[r]_{/M} \arrow[r] & \mfld_{/M} \arrow[ru, "F"'] &  
        \end{tikzcd}
    \end{equation}
    %
    and using the fact that $\disk[r]_{/U} \xrightarrow{} \disk_{/U}$ is final (\cite[prop.2.22]{aft_fhstrat}) immediately gives us that
    %
    \begin{equation}
        F(U) \simeq \mathsf{colim} (\disk_{/U} \xrightarrow{} \disk_{/M} \xrightarrow{F|} \catC) =: \int_U F|.
    \end{equation}
    %
    To preserve the multiplicative structure, these equivalences have to be natural, and there also has to be a commutative diagram
    %
    \begin{equation}\label{eq:mult_strut_comm_square}
        \begin{tikzcd}
            \otimes_i \int_{U_i} F| \arrow[r, "\simeq"] \arrow[d, "\otimes_i \phi (U_i)"', "\simeq"] & \int_{\sqcup_i U_i} F| \arrow[d, "\phi (\sqcup_i U_i)", "\simeq"']\\
            \otimes_i F (U_i) \arrow[r, "\simeq"] & F (\sqcup_i U_i),
        \end{tikzcd}
    \end{equation}
    %
    for each collection of disjoint open sets $\{U_i\}$. Naturality is immediate from the construction because, as already used, each inclusion of open subsets $V \xhookrightarrow{} U$ gives a full subcategory inclusion $\disk[r]_{/V} \xhookrightarrow{} \disk[r]_{/U}$. On the other hand, the existence of the commutative diagram is guaranteed by the equivalence
    %
    \begin{equation}
        \disk[r]_{/\sqcup_i U_i} \xrightarrow{\ \ \simeq \ \ } \bigtimes_i \disk[r]_{/U_i}.
    \end{equation}

@@

\begin{corollary}\label{cor:disk_alg=falg}
    The $\infty$-operad governing factorization algebras on a stratified manifold $M$ can be taken to be $\disk[r]_{/M}$,
    %
    \begin{equation}
        \alg{\disk[r]_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \falg_M (\catC).
    \end{equation}
\end{corollary}

>>>>

Now that we have introduced all the varieties of factorization algebras, it's a natural and useful question to ask what the $\infty$-operad governing them is. For prefactorization algebras, the answer comes by definition, but this is not the case for (locally constant) factorization algebras. We will be working in the generality of stratified manifolds, and all our results in this section will come in pairs, one for the locally constant case and one not. We call the results in the not-necessarily-locally-constant case corollaries since their proofs will be obvious from the proofs of the statements in the locally constant case. To connect factorization algebras to the theory of algebras over an $\infty$-operad we will work in two steps. First we have the following results:
%
\begin{proposition}\label{prop:fh_disk_to_lcfa}
    Given a stratified manifold $M$ factorization homology provides a functor between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$
    %
    \begin{equation}
        \int : \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC).
    \end{equation}
\end{proposition}
%
\begin{corollary}\label{cor:fh_disk_to_falg}
    Given a stratified manifold $M$ factorization homology provides a functor
    %
    \begin{equation}
        \int: \alg{\disk[r]_{/M}} (\catC) \xrightarrow{\ \ \ \ } \falg_{M} (\catC).
    \end{equation}
\end{corollary}

The second step is then showing that the functors constructed above are equivalences, which we summarize in the following results:
%
\begin{theorem}\label{thm:disk_alg=lcfa}
    For each stratified manifold $M$, the previously constructed factorization homology functor provides an equivalence of $\infty$-categories between $\disk_{/M}$-algebras and locally constant factorization algebras on $M$. Equivalently, the $\infty$-operad governing locally constant factorization algebras can be taken to be $\disk_{/M}$
    %
    \begin{equation}
        \alg{\disk_{/M}} (\catC) \xrightarrow[\int]{\ \ \simeq \ \ } \lcfa_M (\catC).
    \end{equation}
\end{theorem}
%
\begin{corollary}\label{cor:disk_alg=falg}
    The $\infty$-operad governing factorization algebras on a stratified manifold $M$ can be taken to be $\disk[r]_{/M}$,
    %
    \begin{equation}
        \alg{\disk[r]_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \falg_M (\catC).
    \end{equation}
\end{corollary}
%
The reason for the phrasing in these results is that, technically speaking, equivalence of the $\infty$-categories of algebras does not imply equivalence of the underlying operads. However since we only defined (locally constant) factorization algebras at the level of algebras and not on the level of $\infty$-operads, we can take the operadic definition as the basic one, and interpret the results as connecting this to the classical definition. The theorems that we present in this section are immensely helpful in relating factorization algebras to results in the area of disk algebras, which will be obvious throughout the rest of this work. One important example that we will see is in \Cref{ch:gluing_disk_alg}.

In the service of working towards proofs of all of these results we first have to pause and develop some necessary technically results regarding Weiss covers.

\begin{lemma}\label{lem:weiss_to_ordinary}
    Let $M$ be a topological space with a sieve $\mathscr{U}$. The following are equivalent:
    %
    \begin{enumerate}
        \item $\mathscr{U}$ is a Weiss sieve of $M$,
        \item for all $n \geq 0$, the sieve $\{ \mathrm{Conf}_n(U)_{\Sigma_n} \xhookrightarrow{} \mathrm{Conf}_n(M)_{\Sigma_n} \mid U \in \mathscr{U} \}$ is a covering sieve of the unordered configuration space $\mathrm{Conf}_n(M)_{\Sigma_n}$ of $n$ points in $M$.
    \end{enumerate}
\end{lemma}

\begin{proof}
    In the forward direction, let $[(x_1, \dots, x_n)] \in \mathrm{Conf}_n(M)_{\Sigma_n}$ be an equivalence class of $n$ points under the action of the symmetric group. By definition of Weiss sieve, there is a $U \in \mathscr{U}$ such that $\{x_1, \dots, x_n\} \subset U$. Since none of the points are the same this means that $(x_1, \dots, x_n) \in U^{\times n}$, and subsequently that $(x_1, \dots, x_n) \in \mathrm{Conf}_n(U)$. Taking quotients we get that $[(x_1, \dots, x_n)] \in \mathrm{Conf}_n(U)_{\Sigma_n}$. Since $\mathrm{Conf}_n(U)_{\Sigma_n}$ is open in the topology of $\mathrm{Conf}_n(M)_{\Sigma_n}$, the collection of these form a covering sieve.

    In the opposite direction, let $S \subset M$ be a finite set with cardinality $|S| = n$. Naming its elements $x_1, \dots, x_n$ in an arbitrary order that will not matter because of the $\Sigma_n$ quotient, we get the $[(x_1, \dots, x_n)] \in \mathrm{Conf}_n(M)_{\Sigma_n}$. By assumption there exists a $U \in \mathscr{U}$ such that $[(x_1, \dots, x_n)] \in \mathrm{Conf}_n(U)_{\Sigma_n}$. In particular, this means that $(x_1, \dots, x_n) \in U^{\times n}$, or in other words that $x_i \in U$ for all $1 \leq i \leq n$. This implies that $\mathscr{U}$ satisfies the Weiss property.
\end{proof}

\begin{lemma}\label{lem:gluing_disk/M}
    A Weiss sieve $\mathscr{U} \subset \mfld[r]_{/M}$ canonically determines a morphism
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r] \xrightarrow{\disk_{/-}} \mathsf{RFib}_{\disk(\bstr)}) \xrightarrow{\ \ \simeq \ \ } \disk_{/M}
    \end{equation}
    of right fibrations over $\disk(\bstr)$, which moreover, is an equivalence.
\end{lemma}

\begin{proof}
    The morphism is determined by the universal property of the colimit with the component maps $\disk_{/U} \xrightarrow{} \disk_{/M}$ given from the open embeddings $U \xhookrightarrow{} M$. To show the equivalence, we follow the strategy laid out in part 2 of the proof of \cite[Prop.2.22]{af_primer}, while at the same time adapting it to the stratified setting. A morphism of right fibrations, as in the statement, is an equivalence if, and only if, it is so when looked at as a right fibration over the maximal $\infty$-groupoid of the base (cite ...). In our case this is\footnote{Specifically, the wreath product of groups in the notation is referring to $\mathsf{End}_{\bstr}(U) \wr_{\{1, 2, \dots, i\}} \Sigma_i$, the one whose underlying set is $\mathsf{End}_{\bstr}(U)^{\times \{1, 2, \dots, i\}} \times \Sigma_i$.}
    %
    \begin{equation}
        \disk(\bstr)^{\simeq} \simeq \coprod_{i \geq 0} \prod_{[U]} \mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i),
    \end{equation}
    %
    as given by \cite[Lem.2.21]{aft_fhstrat}. The same lemma also tells us that the maximal $\infty$-groupoid of $\disk_{/M}$ is given by\footnote{The notation $M_{[U]}$ denotes the $[U]$-stratum of the stratified manifold $M$, which is a \emph{smooth} manifold, as defined in \cite[Def.4.4.5]{aft_localstrut}.}
    %
    \begin{equation}
        \disk_{/M}^{\simeq} \simeq \coprod_{i \geq 0} \prod_{[U]} \mathrm{Conf}_{i}(M_{[U]})_{\Sigma_i}.
    \end{equation}
    %
    In both cases, the product runs over isomorphism classes of basics. It is also clear that the map $\disk_{/M}^{\simeq} \xrightarrow{} \disk(\bstr)^{\simeq}$ resulting from the right fibration from the slice respects this decomposition in that there result maps of spaces
    %
    \begin{equation}
        \mathrm{Conf}_i(M_{[U]})_{\Sigma_i} \xrightarrow{\ \ \ \ } \mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i),
    \end{equation}
    %
    for each $i \geq 0$, and each isomorphism class $[U]$ of basics in $\bstr$. Thus, working piece by piece, we need to show that
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\mathrm{Conf}_{i}(-_{[U]})_{\Sigma_i}} \mathsf{Sp}_{/\mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i)}) \xrightarrow{\ \ \simeq \ \ } \mathrm{Conf}_{i}(M_{[U]})_{\Sigma_i},
    \end{equation}
    %
    for all $i$ and $[U]$ as specified before, where we notice that the decomposition into maps of spaces means that our target is even $\mathsf{Sp}_{/\mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i)}$ and not just right fibrations. We will first explain this equivalence at the level of spaces and only after will we argue why the equivalence respects the maps to $\mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i)$. From a Weiss sieve $\mathscr{U}$ of $M$ we easily get a Weiss sieve $\mathscr{U}_{[U]}$ of $M_{[U]}$ by intersecting with $M_{[U]}$ as a submanifold of $M$. Using $\mathscr{U}_{[U]}$, we define $\mathscr{U}_{i, [U]}$ to be the sieve of $\mathrm{Conf}_i(M_{[U]})_{\Sigma_i}$ as in \Cref{lem:weiss_to_ordinary}. These considerations give us equivalences
    %
    \begin{align}\label{eq:ord_to_W_equivs}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\mathrm{Conf}_{i}(-_{[U]})_{\Sigma_i}} \mathsf{Sp}) &\simeq \mathsf{colim} (\mathscr{U}_{[U]} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\mathrm{Conf}_{i}(-)_{\Sigma_i}} \mathsf{Sp})\notag\\
        &\simeq \mathsf{colim} (\mathscr{U}_{i,[U]} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{} \mathsf{Sp}).
    \end{align}
    %
    The second equivalence in the above is simply a statement about the unions over the two covers and is a restatement of \Cref{lem:weiss_to_ordinary}. But, by \cite[Prop.A.3.2]{lurie_ha} there is an equivalence
    %
    \begin{equation}\label{eq:gluing_top_lurie}
        \mathsf{colim} (\mathscr{U}_{i,[U]} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{} \mathsf{Sp}) \xrightarrow{\ \ \simeq \ \ } \mathrm{Conf}_{i}(M_{[U]})_{\Sigma_i}.
    \end{equation}
    %
    It is obvious that the equivalences in \Cref{eq:ord_to_W_equivs} lie over $\mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i)$, since they're nothing more than a rewriting. The equivalence in \Cref{eq:gluing_top_lurie} also lies over $\mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i)$ because all the various pieces that we're gluing in $\mathsf{Sp}$ come from unordered configuration space manifolds............. 
\end{proof}

\begin{remark}
    That the maps to $\mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i)$ don't play much of a role can also be seen through the fact that this is the only place where the choice of tangential structure $\bstr$ enters the discussion in the form of including or excluding certain endomorphisms. 
\end{remark}

\begin{proof}[Proof of {\Cref{prop:fh_disk_to_lcfa}}]
    We adopt a proof strategy similar to \cite[prop.3.14]{af_primer}. Unlike there, we work in the relative case of $\disk_{/M}$ instead of $\disk(\bstr)$. Since the $\infty$-category of factorization algebras is defined as a pullback, we will look for a commutative diagram involving $\alg{\disk_{/M}}$, so that, by the universal property of the pullback, we get the stated functor.

    We first observe that, by definition, the $\infty$-operad $\opens(M) := \mfld[r]_{/M}$. There are clear functors of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \xhookrightarrow{\ \ \ } \mfld_{/M} \xleftarrow{\ \ \ } \mfld[r]_{/M}.
    \end{equation}
    %
    At the level of algebras over them, they give rise to the commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}
            \alg{\disk_{/M}} (\catC) \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l] \arrow[r] & \mathsf{Fun}(\opens(M), \catC),
        \end{tikzcd}
    \end{equation}
    %
    where the vertical arrows are forgetful functors. Factorization homology as a left Kan extension gives one the adjoints indicated below
    %
    \begin{equation}
        \begin{tikzcd}[row sep = large, column sep = large]
            \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10, "\int"] \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) \arrow[r, bend left=10, "\int"] & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l, bend left=10] \arrow[r] & \mathsf{Fun}(\opens(M), \catC).
        \end{tikzcd}
    \end{equation}
    %
    A result found in \cite[thm.1.2.5]{aft_localstrut} (where they use slightly different notation and call locally constant sheaves constructible) gives us the equivalence
    %
    \begin{equation}
        \csheaves[W](\mfld_{/M}, \catC) \simeq \csheaves[W, lc](\mfld[r]_{/M}, \catC) =: \csheaves[W, lc]_M(\catC),
    \end{equation}
    %
    which at the level of underlying functors, is exactly the restriction along the functor $\opens(M) \xrightarrow{} \mfld_{/M}$, so that we can append this to our commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}[row sep = large, column sep = large]
            \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10, "\int"] \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) \arrow[r, bend left=10, "\int"] \arrow[dr, dashed] & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l, bend left=10] \arrow[r] & \mathsf{Fun}(\opens(M), \catC) \\
            & \csheaves[W](\mfld_{/M}, \catC) \arrow[r, "\simeq"] \arrow[u] & \csheaves[W, lc]_M(\catC) \arrow[u].
        \end{tikzcd}
    \end{equation}
    %
    If we can find the dashed functor which makes the diagram commute, as indicated above, we would be done with the construction. This amounts to showing that the left Kan extension $\int F$ of a functor $F \in \mathsf{Fun}(\disk_{/M}, \catC)$ along $\disk_{/M} \xhookrightarrow{} \mfld_{/M}$ is automatically a Weiss cosheaf. By the definition of $\csheaves[W](\mfld_{/M}, \catC)$, this means that the restriction of $\int F$ to $\mathsf{Fun}(\mfld[r]_{/M}, \catC)$ satisfies the cosheaf property for every Weiss sieve $\mathscr{U} \subset (\mfld[r]_{/M})_{/e}$, where $e:N \xhookrightarrow{} M$ is an open embedding. Here we notice that for the Weiss property to even make sense, we are implicitly using \Cref{lem:double_slice}, so that the Weiss sieve $\mathscr{U}$ is defined as a subcategory of $\mfld[r]_{/N}$.

    A similar calculation appears in part 2 of the proof of \cite[prop.2.22]{af_primer}, with the caveat that there things are presented for smooth manifolds. However, because of \Cref{lem:weiss_to_ordinary} and \Cref{lem:gluing_disk/M} we can adapt the proof to the stratified setting as well. Namely, we're trying to show that the canonical map 
    %
    \begin{equation}\label{eq:fhfunc_canonical_map}
        \mathsf{colim}(\mathscr{U} \xhookrightarrow{} \mfld[r]_{/N} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC) \xrightarrow{\ \ \ \ } \int_e F
    \end{equation}
    %
    is an equivalence for each sieve $\mathscr{U}$. Since $\catC$ has all relevant colimits the left Kan extension $\int F$ is given pointwise by
    %
    \begin{equation}
        \int_e F \simeq \mathsf{colim} (\disk_{/N} \xrightarrow{\simeq} (\disk_{/M})_{/e} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC),
    \end{equation}
    %
    and this allows us to rewrite our canonical map from \Cref{eq:fhfunc_canonical_map} into
    %
    \begin{align}
        \mathsf{colim} \Big( \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\disk_{/-}} \cat) \xrightarrow{} &\disk_{/N} \rightarrow \disk_{/M} \xrightarrow{F} \catC \Big)\notag\\
        \xrightarrow{\ \ \ \ \ } \mathsf{colim} (&\disk_{/N} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC).
    \end{align}
    %
    However, the statement of \Cref{lem:gluing_disk/M} is exactly the statement that the above map is an equivalence.
\end{proof}

@@

\begin{proof}[Proof of {\Cref{thm:disk_alg=lcfa}}]
    To show essential surjectivity of $\int$, for each $F \in \lcfa_M (\catC)$ we will find an equivalence $\int F| \simeq F$ in $\lcfa_M (\catC)$, with $F|$ to be defined later. Since $\lcfa_M (\catC) \xrightarrow{} \alg{\opens(M)}$ is fully faithful, this amounts to finding equivalences of prefactorization algebras, namely a family of equivalences
    %
    \begin{equation}
        \int_U F| \xrightarrow[\simeq]{\ \ \phi (U) \ \ } F(U),
    \end{equation}
    %
    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which preserve the multiplicative structure (see \Cref{cd:fa_morphisms}). Since $F$ is a locally constant factorization algebra the functor
    %
    \begin{equation}
        \lcfa_M (\catC) \xrightarrow{} \csheaves[W, lc](\mfld[r]_{/M}, \catC) \simeq \csheaves[W](\mfld_{/M}, \catC) \xrightarrow{} \mathsf{Fun}(\mfld_{/M}, \catC),
    \end{equation}
    %
    which we omit in the notation, allows us to consider $F$ as a functor from $\mfld_{/M}$. Furthermore, since $\disk[r]_{/U}$ is a Weiss sieve we can write
    %
    \begin{align}
        F(U) &\simeq \mathsf{colim} (\disk[r]_{/U} \xrightarrow{} \disk[r]_{/M} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{F} \catC).
    \end{align}
    %
    By consulting the commutative diagram
    % 
    \begin{equation}
        \begin{tikzcd}
            \disk[r]_{/U} \arrow[d] \arrow[r] & \disk_{/U} \arrow[d] & \\
            \disk[r]_{/M} \arrow[d] \arrow[r] & \disk_{/M} \arrow[d] \arrow[r, "F|"] & \catC, \\
            \mfld[r]_{/M} \arrow[r] & \mfld_{/M} \arrow[ru, "F"'] &  
        \end{tikzcd}
    \end{equation}
    %
    and using the fact that $\disk[r]_{/U} \xrightarrow{} \disk_{/U}$ is final (\cite[prop.2.22]{aft_fhstrat}) immediately gives us that
    %
    \begin{equation}
        F(U) \simeq \mathsf{colim} (\disk_{/U} \xrightarrow{} \disk_{/M} \xrightarrow{F|} \catC) =: \int_U F|.
    \end{equation}
    %
    To preserve the multiplicative structure, these equivalences have to be natural, and there also has to be a commutative diagram
    %
    \begin{equation}\label{eq:mult_strut_comm_square}
        \begin{tikzcd}
            \otimes_i \int_{U_i} F| \arrow[r, "\simeq"] \arrow[d, "\otimes_i \phi (U_i)"', "\simeq"] & \int_{\sqcup_i U_i} F| \arrow[d, "\phi (\sqcup_i U_i)", "\simeq"']\\
            \otimes_i F (U_i) \arrow[r, "\simeq"] & F (\sqcup_i U_i),
        \end{tikzcd}
    \end{equation}
    %
    for each collection of disjoint open sets $\{U_i\}$. Naturality is immediate from the construction because, as already used, each inclusion of open subsets $V \xhookrightarrow{} U$ gives a full subcategory inclusion $\disk[r]_{/V} \xhookrightarrow{} \disk[r]_{/U}$. On the other hand, the existence of the commutative diagram is guaranteed by the equivalence
    %
    \begin{equation}
        \disk[r]_{/\sqcup_i U_i} \xrightarrow{\ \ \simeq \ \ } \bigtimes_i \disk[r]_{/U_i}.
    \end{equation}

@@
